WASP-4 is Accelerating Towards the Earth

### 2020-01-25 paper/ms.tex
eccentricities: planets and stars be different

To derive constraints on possible companion masses and separations
from the radial velocities, we followed the procedure of
\citet{bryan_excess_2019}.  We began by defining a $75\times50$ grid
in true planetary mass and semimajor axis, with even logarithmic
spacing from 1 to 900$\,$$M_{\rm Jup}$ and 3 to 500$\,$${\rm AU}$.  We
then considered the possibility that an additional companion in any
particular cell could explain the observed linear trend.  In each
cell, we simulated 500 hypothetical companions.

We assigned each companion a mass and semimajor axis from log-uniform
distributions within the grid cell. We drew the inclination from a
uniform distribution in $\cos i$.  The eccentricity was drawn from
\citet{kipping_beta_2013}'s long-period exoplanet Beta distribution
($a=1.12$, $b=3.09$).  For each simulated companion, we then drew a
sample from the converged chains of our initial model of WASP-4b, plus
its linear trend. We subtracted the planet's orbital solution, leaving
the linear trend.  Given $(a_{\rm c}, M_{\rm c}, e_{\rm c}$ for each
simulated outer companion, and the fixed instrument offsets and
jitters from the MCMC chains, we then performed a maximum likelihood
fit for the time and argument of periastron of the outer simulated
companion.  We converted the resulting $50\times50\times500$ cube of
best-fit log-likelihood values to probabilities, and averaged over the
samples in each grid cell to derive a probability distribution in mass
and semi-major axis.

>>>>

To derive constraints on possible companion masses and separations
from the radial velocities, we mostly followed the procedure of
\citet{bryan_excess_2019}.

We began by defining a $75\times50$ grid in true planetary mass and
semimajor axis, with even logarithmic spacing from 1 to 900$\,$$M_{\rm
Jup}$ and 3 to 500$\,$${\rm AU}$.  We then considered the possibility
that an additional companion in any particular cell could explain the
observed linear trend.  In each cell, we simulated 500 hypothetical
companions.

%FIXME: may want to verify that changing the cutoff location, to say
%80Mjup or whatever the minimum BD mass is doesn't drastically alter
%the posterior
We assigned each companion a mass and semimajor axis from log-uniform
distributions within the grid cell. We drew the inclination from a
uniform distribution in $\cos i$.  For companion masses less than
$10\,M_{\rm Jup}$, we drew the eccentricity from
\citet{kipping_beta_2013}'s long-period exoplanet Beta distribution
($a=1.12$, $b=3.09$).  If the companion mass exceeded $10\,M_{\rm
Jup}$, we drew the eccentricity distribution from the power-law $p_e
\propto e^\eta$ reported by \citet{moe_mind_2017} in their
Equation~17.  We emphasize that the long-period exoplanet and
long-period binary distributions are quite different: the exoplanet
distribution is ``bottom-heavy'', with eccentricities preferentially
close to zero. The binary star distribution is ``top-heavy'', with
more eccentricities close to one.  We chose a mass cutoff of
$10\,M_{\rm Jup}$ based on the bound observed by
\citet{schlaufman_evidence_2018} between giant planets, presumably
formed through core accretion, and brown dwarfs, presumably formed via
gravitational instability.

For each simulated companion, we then drew a sample from the converged
chains of our initial model of WASP-4b, plus its linear trend. We
subtracted the planet's orbital solution, leaving the linear trend.
Given $(a_{\rm c}, M_{\rm c}, e_{\rm c}$ for each simulated outer
companion, and the fixed instrument offsets and jitters from the MCMC
chains, we then performed a maximum likelihood fit for the time and
argument of periastron of the outer simulated companion.  We converted
the resulting $75\times50\times500$ cube of best-fit log-likelihood
values to probabilities, and averaged over the samples in each grid
cell to derive a probability distribution in mass and semi-major axis.
